Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-05-07 Ben_Manuscripts/stochastic_transport/arxiv/ms.tex
Filling in missing parts of draft

\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb,footinbib]{revtex4-2}
\usepackage{CJK}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

@@

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores.

@@

  Next, we generalize Markov state models, treating the
  configurational states of the system as a Markov process where each
  state has distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness.

  Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

@@

  Highly selective separations membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
  the materials industry, there is a strong interest in creating breathable
  fabrics which selectively allow passage of water
  vapor.~\cite{mondloch_destruction_2015}

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate
  solute-specific separation membranes using the available chemical space of
  LLC monomers. To date, only a limited subset of LLC monomers have been
  studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. We chose to study the
  H\textsubscript{II} phase because it is a simpler geometry to model than the
  Q\textsubscript{I} phase and significantly more structural data is available
  to help ensure molecular models are consistent with experiment. In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
% BJC2: removed this sentence. High uncertainty MSDs don't really relate to long timescale predictions. Unless the MSDs were linear.
%  This results in relatively high uncertainties in observables such as mean
%  squared displacement (MSD), preventing reliable long timescale predictions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.  
  %BJC2: following sentence replaced with above
%  We are in need of a way of studying the collective motion of a much larger
%  set of solutes over much longer timescales.
  %MRS11: Maybe this last sentence could be changed. Because you aren't really finding a way to study larger sets of 
  %solutes over larger timescales, you are using a limited amount of atomistic simulation into long time scale behavior efficiently. We can discuss variations as needed!

  %BJC: maybe this paragraph can be cut down?
  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  %MRS11: this next sentence could probably be cut - it's kind of vague.
  %BJC2: True
%  The complexity of a well-fit model generally parallels the complexity of the
%  transport mechanism being studied, as well as the transport information the
%  model conveys. 
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  %MRS11: in this paragraph, the ``we can'' is vague, and doesn't
  %ascribe agency.  Is ``We'' our group? Is it the field as whole?
  %If it's something someone has done in the past, there should be
  %citations. If it's something that can be done in the future, the
  %phrasing should be a long the lines of ``it is possible to'', ``it
  %can be done'', etc.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. Fortunately, there is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations.

  % BJC: I'd say this is where the intro starts to get technical
%  We constructed our first model by applying the existing rigorous theoretical
%  foundation which describes the motion of particles that exhibit non-Brownian,
%  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
%  introduced by fractional calculus are instrumental to this
%  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
%  normally linear diffusion equation to fractional derivative orders, providing
%  descriptions of a much more diverse set of behavior, including subdiffusion,
%  a type of anomalous diffusion exhibited by solutes in this
%  study.~\cite{klages_anomalous_2008}

  %MRS11: should be clear if first model is previous publications, or what is presented here.
  %If what is presented here, should talk about how it will be presented, not that it was developed. 
  %MRS11: research activities happened in the past, presentation of research is described in the present.
  %or potentially future if describing what will be presented in the rest of the paper. 
  %BJC: replacement to above.
  %BJC1: Made clear that this is talking about the first model of this work.
  %BJC1: went through rest of intro to make sure tense is consistent
  The first model that we develop in this work allows us to characterize the 
  hopping and trapping behavior displayed by solutes in our MD simulations. This 
  type of non-Brownian dynamical behavior results in subdiffusive transport which
  is well-described by anomalous diffusion (AD) theory.~\cite{metzler_random_2000,bouchaud_anomalous_1990,klages_anomalous_2008}
  %MRS12: removing paragraph break
  % BJC: focused following paragraph (RWF doesn't need to be talked about) and 
  % stole thesis from paragraph below it
  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

%  Three well-known classes of behavior leading to anomalous subdiffusion are
%  continuous time random walks (CTRWs), fractional Brownian motion (FBM) and
%  random walks on fractals (RWFs).\cite{meroz_toolbox_2015} These types of
%  motion are frequently used alone or in combination to describe single
%  particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014} A CTRW
%  is characterized by a distribution of hop lengths and dwell times, where
%  trajectories consist of sequential independent random draws from each
%  distribution.\cite{montroll_random_1965} FBM is common in crowded,
%  viscoelastic environments where each jump comes from a Gaussian distribution
%  but is anti-correlated to its previous
%  steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
%  An RWF is imposed by a system's geometry. Systems with tortuous pathways and
%  dead ends cause anti-correlated
%  motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

%  We treated our system as an FBM process subordinate to a CTRW, or
%  subordinated FBM (sFBM) for short. 
  We fit sFBM models in two ways: First, we parameterize solute motion using
  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
  Second, we use a two-state approach by extracting two sets of model parameters
  calculated based on a solute's radial distance from the closest pore center. 
  This allows us to include the different dynamical behavior of solutes previously
  observed within the pore region versus within the monomer tails.

  Where sufficiently close to observed data, these fitted sFBM models
  provide a way to propagate information about solute trajectories gathered 
  at the microsecond time scale to realistic experimental time scales. 
  They can also confirm the importance of assumed solute-membrane interactions 
  used to define the model's functional form, and
  suggest missing components. They can help researchers formulate hypotheses to
  explain why a certain set of parameters is characteristic to a specific
  solute.

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Rather than using them to calculate 
  diffusion constants or to relate our simulations to experimental measurements, we
  compare MSDs calculated from MD simulations to those generated from our models 
  in order to validate those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories.

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the ensemble averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory.

  The time averaged and ensemble averaged MSDs will give identical results 
  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
  law distribution of trapping times leads to weak ergodicity breaking.
  In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
  power law trapping behavior, the time between hops diverges so there is no 
  characteristic measurement time scale of solute motion. In fact, as measurement 
  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
  aging, because trajectories with trapping times on the order of the measurement 
  time get incorporated into the calculation.~\cite{bel_weak_2005}

  We chose to use just the time-averaged MSD to compare MD trajectories with
  modeled trajectories, because, compared to the ensemble average, it is a more
  statistically robust measure of the average distance a solute travels over
  time. The ensemble MSD of only 24 solute trajectories would have much higher
  uncertainties.

@@

  sFBM implies that hops are correlated which we describe using the Hurst
  parameter, $H$. The autocovariance function of hop lengths has the
  analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from
  which hops are drawn and $k$ is the time lag, or number of increments between
  hops. The hop autocorrelation function is simply
  Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance.  When $H <
  0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian
  motion and when $H > 0.5$, one observes positive correlation between hops.

>>>>

%\documentclass[aps,pre,twocolumn,showpacs,preprintnumbers,amsmath,amssymb,footinbib]{revtex4-1}
\documentclass[journal=ancac3,manuscript=article,layout=twocolumn]{achemso}
%\usepackage{CJK}

\let\titlefont\undefined
\makeatletter
\let\l@addto@macro\relax
\makeatother
\usepackage[fontsize=10pt]{scrextend}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage[caption=false]{subfig}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{diagbox}
\usepackage{array}

\SectionNumbersOn

\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

@@

  Mathematically modeling complex transport phenomena can be a powerful tool
  for extracting important physical information from molecular simulations. 
  In this study, we present two new approaches that use stochastic time series
  modeling to predict long time-scale behavior and macroscopic properties 
  from molecular simulation which can be generalized to other molecular systems
  where complex diffusion occurs. Specifically, we parameterize our models using
  long molecular dynamics (MD) simulation trajectories of a cross-linked 
  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
  predict solute mean squared displacements (MSDs), solute flux, and
  solute selectivity in macroscopic length pores.

@@

  Next, we present an approach that generalizes Markov state models, treating 
  the configurational states of the system as a Markov process where each 
  state has distinct transport properties. For each state and transition between
  states, we parameterize the distribution and temporal correlation structure of
  positional fluctuations as a means of characterization and to allow us to
  predict solute MSDs.

  We show that both stochastic models reasonably reproduce the MSDs calculated 
  from MD simulations. However, qualitative differences between MD and Markov 
  state dependent model-generated trajectories may in some cases limit their 
  usefulness. With these parameterized stochastic models, we demonstrate how 
  one can estimate flux of a solute across a macroscopic-length pore and, based
  on those quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent solute 
  motions that do not follow simple diffusive behavior with long time-scale 
  behavior, in an approach generalizable to many types of molecular systems 
  with complex dynamics.

@@

  There is a large disparity between the time scales accessible to atomistic 
  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
  over nanoseconds of simulation may tell a very different story than that 
  inferred by bulk measurements on the time-scale of seconds. Understanding 
  complex dynamical behavior on short time-scales and connecting them with much
  longer time-scales can provide fundamental insight which can be used for 
  atomic level design of materials. In this work, we pursue this connection 
  applied to highly selective aqueous filtration membranes and demonstrate how
  one can gain chemical intuition which serves both theoretical and experimental
  researchers.

  Highly selective separation membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} 
  %BJCB: could cut this last sentence. It's kind of awkward  
  %MRSB: agree  
  %In the materials industry, there is a strong interest in creating breathable
  %fabrics which selectively allow passage of water
  %vapor.~\cite{mondloch_destruction_2015}

  % BJCA: I could likely condense this paragraph to focus primarily on the HII phase
  % and its complex pores.
  %MRS: yes.  QI not relevant
%  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
%  can be cross-linked into mechanically strong and highly selective nanoporous
%  membranes.~\cite{gin_polymerized_2008} They may provide a promising
%  alternative to conventional membrane separation techniques by being selective
%  based not only on solute size and charge, but on solute chemical
%  functionality as well.~\cite{dischinger_application_2017} One can tune the
%  functionality of LLC monomers in order to enhance or weaken specific
%  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
%  morphologies of LLC membranes are being actively developed. The inverted
%  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
%  pores on the order of 1 nm in size. A perfectly synthesized
%  H\textsubscript{II} phase has an ideal geometry for high throughput
%  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
%  a large scale as required for high permeability has shown limited
%  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
%  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
%  complex pores of the H\textsubscript{II} phase but its geometry consists of a
%  tortuous network of 3D interconnected pores which do not require
%  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
%  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
%  H\textsubscript{II} phase, it is considerably easier to produce 
%  at scale.~\cite{hatakeyama_nanoporous_2010}

  %BJCB: removed discussion of Q1 from above paragraph
  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017}

  % BJCB: split into two paragraphs  
  In this work, we study the inverted hexagonal, H\textsubscript{II}, LLC phase. 
  The H\textsubscript{II} phase has densely packed, uniform-sized pores on the 
  order of 1 nm in size. A perfectly aligned H\textsubscript{II} phase has 
  an ideal geometry for high throughput separations.~\cite{feng_scalable_2014,feng_thin_2016}

  Molecular modeling may make it possible to efficiently evaluate solute-specific
  separation membranes using the available chemical space of LLC monomers by 
  allowing researchers to understand their macroscopic behavior based on 
  microscopic, chemically-dependent solute motions. To date, only a limited 
  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. 
  %We chose to study the
  %H\textsubscript{II} phase because it is a simpler geometry to model than the
  %Q\textsubscript{I} phase and significantly more structural data is available
  %to help ensure molecular models are consistent with experiment. 
  In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.

  Mathematical descriptions of transport in complex separations membranes are a
  powerful way to understand mechanisms and formulate design principles.
  \cite{vinh-thang_predictive_2013,geens_transport_2006,darvishmanesh_mass_2016}
  In dense homogeneous membranes, the solution-diffusion model
  can extract diffusion and partition coefficients and has successfully
  predicted solute transport rates.~\cite{wijmans_solution-diffusion_1995}
  Analogously, pore-flow models yield predictions of diffusion coefficients and
  solute transport rates in nanoporous membranes.~\cite{paul_diffusive_1974}
  Modern single particle tracking approaches have taken researchers beyond
  continuum modeling allowing them to characterize complex diffusive
  behavior.~\cite{manzo_review_2015} At the molecular level, one can use
  molecular dynamics (MD) simulations to study both single particle dynamics
  and bulk transport properties with atomic-level
  insight.~\cite{coscia_chemically_2019,maginn_best_2018} All of these
  approaches facilitate generation of hypotheses about the molecular origins of
  separations by attempting to give a more intuitive understanding of how
  solutes move as a function of their environment, in turn suggesting
  experiments that could be performed.

  Using a bottom-up modeling approach, it may be possible to parameterize single
  particle behavior by extracting particle trajectories from MD simulations and
  studying the properties that have the greatest influence on solute dynamics.
  With this information, one can learn how to construct an ensemble of characteristic
  single solute trajectories with these properties which would be useful for
  making long timescale predictions with computational ease and lower
  uncertainties. There is an abundance of information encoded in
  the complex solute trajectories. One can incorporate fluctuations and 
  time-dependent correlations in solute position into transport models, 
  as well as the length of time solutes are trapped. It is possible to add further
  detail by integrating this time series analysis with existing knowledge of the
  primary trapping mechanisms as well as the solute's changing chemical environment
  within the heterogeneous membrane.

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
  these fitted models provide a way to propagate information about solute 
  trajectories gathered at the microsecond time scale to realistic experimental 
  time scales.

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
  The tools introduced by fractional calculus are instrumental to this 
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
  linear diffusion equation to fractional derivative orders, providing descriptions
  of a much more diverse set of behavior, including subdiffusion, a type of 
  anomalous diffusion exhibited by solutes on the simulation time scales of this
  study.~\cite{klages_anomalous_2008}

  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

% BJCC: I cut this, doesn't really seem to be necessary for intro
%  We fit sFBM models in two ways: First, we parameterize solute motion using
%  a single set of parameters fit to a hypothesized anomalous diffusion (AD) model.
%  Second, we use a two-state approach by extracting two sets of model parameters
%  calculated based on a solute's radial distance from the closest pore center. 
%  This allows us to include the different dynamical behavior of solutes previously
%  observed within the pore region versus within the monomer tails.

@@

  On the time scales simulated in this study, solutes in this system very 
  clearly exhibit subdiffusive behavior, a type of anomalous diffusion. 
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of 
  the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. It is also possible that solute dynamics will become diffusive on
  long simulation timescales. Therefore, the transition from subdiffusion to regular
  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD
  curves. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions as described in subsequent sections.

  % BJCB: condensed commented out section that follows into this paragraph
  In this study, we primarily use the MSD as a tool for characterizing the average
  dynamic behavior of solute trajectories. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled trajectories and
  directly observed MD trajectories. We chose to calculate the time-averaged MSD from 
  our MD simulations and stochastic models which measures all observed displacements
  over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory. In some situations, it may make
  more sense to use the ensemble MSD. We present further discussion of this
  choice in Section~\ref{S-section:msd} of the Supporting Information.

  % BJCA: Could move most of the following discussion to the SI and just present the time-averaged MSD.
  % MRS: good call.

%  In this study, we primarily use the MSD as a tool for characterizing the average
%  dynamic behavior of solute trajectories. Rather than using them to calculate 
%  diffusion constants or to relate our simulations to experimental measurements, we
%  compare MSDs calculated from MD simulations to those generated from our models 
%  in order to validate those models. Therefore, it is only important that we use a
%  consistent definition for calculating the MSD between modeled trajectories and
%  directly observed MD trajectories.
%
%  One can measure MSD in two ways. The ensemble averaged MSD measures 
%  displacements with respect to a particle's initial position:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation}
%  Fits to the ensemble averaged MSD will always reproduce the form of 
%  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
%  displacements over time lag $\tau$: 
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \label{eqn:tamsd}
%  \end{equation}
%  where T is the length of the trajectory. 
%  
%  The time averaged and ensemble averaged MSDs will give identical results 
%  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
%  law distribution of trapping times leads to weak ergodicity breaking.
%  In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
%  power law trapping behavior, the time between hops diverges so there is no 
%  characteristic measurement time scale of solute motion. In fact, as measurement 
%  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
%  aging, because trajectories with trapping times on the order of the measurement 
%  time get incorporated into the calculation.~\cite{bel_weak_2005}
%  
%  We chose to use just the time-averaged MSD to compare MD trajectories with
%  modeled trajectories, because, compared to the ensemble average, it is a more
%  statistically robust measure of the average distance a solute travels over
%  time. The ensemble MSD of only 24 solute trajectories would have much higher
%  uncertainties.

@@

  sFBM implies that hops are correlated which we describe using the Hurst
  parameter, $H$. The autocovariance function of hop lengths has the
  analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from
  which hops are drawn and $k$ is the time lag, or number of increments between
  hops. The hop autocorrelation function is simply
  Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance.  When $H <
  0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian
  motion and when $H > 0.5$, one observes positive correlation between hops. 
  We obtained $H$ by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first ten 0.5 ns time lags of 
  the empirically measured autocorrelation function (see section~\ref{S-section:H_estimate}
  of the Supporting Information for a more in depth justification of this method).
